---
title: "p8105_hw1_ht2611.Rmd"
author: "ht2611"
date: "2022-09-20"
output: github_document
---

P1
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
nrow(penguins)
ncol(penguins)
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,color=species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

The variables are species, island, bill_length_mm, bill_depth_mm 
flipper_length_mm, body_mass_g, sex, year. The nrow is 344, the ncol is 8, 
the mean flipper length is 200.9.

P2
```{r}
library(tidyverse)
example_df = tibble(
  rs=rnorm(10),
  vec_logical = (rs>1),
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "m", "n"),
  vec_factor = factor(c("level1", "level2", "level2", "level2", "level2", "level2", "level2", "level2", "level2", "level3"))
)
mean(example_df$rs)
mean(example_df$vec_logical)
mean(example_df$vec_char)
mean(example_df$vec_factor)
as.numeric(example_df$rs)
as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```

For mean, random sample and logical vector work, character vector and factor vector don't work.
For convertion, only character vector does not work.Because it is defined as character for system and could not be ordered.